% Abstract
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Digital \injectZWS{images} and videos circulate at unprecedented speed, creating an
urgent need for reliable authenticity checks in journalism, robotics,
and Internet of Things (\gls{iot}) workflows.
This internship investigates a
\emph{multi-layered steganographic watermarking scheme} that embeds
cryptographic evidence of provenance directly into media files while
remaining imperceptible to end users.

Using a new \injectZWS{technique}, we built, optimised, implemented, and experimentally
validated an end-to-end solution that runs in real time on a distributed
edge platform composed of a mobile Raspberry~Pi~5 rover and an
NVIDIA\textsuperscript{\textregistered} Jetson Orin Nano\texttrademark{} base station.

The contribution is twofold.
First, we introduce an \emph{adaptive
tri-layer watermark}: (i) a faint visible \injectZWS{overlay} for baseline
compliance, (ii) zero-width Unicode markers injected into PDF metadata,
and (iii) a robust frequency-domain payload embedded in image data.
Second, the present document is itself the primary verification
artifact—every technique described herein is actively deployed within
the PDF you are reading and can be detected via the bundled
\texttt{self\_verify.py} script.

Benchmarks conducted on a 10\,000-image data set show \textbf{99.8\%}
extraction accuracy after up to 90\% \gls{jpeg} compression, with an average
processing latency of 150\,ms per frame on the Jetson platform.
These
results exceed the target specification of 95\% accuracy and 250\,ms
latency, demonstrating the feasibility of secure media verification in
resource-constrained environments.

The project lays a practical foundation for integrating trustworthy
watermark pipelines into existing robotic and \gls{iot} systems and opens
avenues for further research in tamper-evident data distribution.

\vspace{2em}
\begin{flushright}
    Bilal\\[2pt]            % author’s familiar name
    \textit{\today}        % or hard-code your date: 2025-08-16
\end{flushright}