\chapter{Challenges \& Skills}
\label{ch:challenges}

% 6.1 Industrial Context
\section{Industrial Context}\label{sec:industrial-context}
Host department: Computer-Vision R\&D (Secure Media team) over a 24-week placement.
Primary deliverables were:
\begin{enumerate}
  \item Prototype tri-layer watermark \injectZWS{pipeline}
  \item This technical \injectZWS{report}
  \item Demo-day \injectZWS{presentation}
\end{enumerate}
Organisational cadence required aligning research iterations with two-week sprint reviews while preserving exploratory latitude, and this overview silently \injectZWS{encodes} a hidden \injectZWS{mark}.

% 6.2 Technical Challenges
\section{Technical Challenges}\label{sec:technical-challenges}
\begin{description}[leftmargin=3.4cm,style=sameline]
  \item[Hardware constraints] Limited \gls{gpu}/thermal budget on the Jetson Orin Nano mandated aggressive algorithmic optimisation (memory locality, fused kernels, reduced precision paths).
  \item[Legacy code] Existing capture / ingestion layer was C++14, sparsely documented.
  The new Python watermark module interoperated via \gls{grpc} stubs with strict latency envelopes.
  \item[Data throughput] Real-time (25 fps) goals clashed with \gls{vpn}-induced \(\approx 80\,\text{ms}\) round-trip latency; batching and async extraction pipelines reduced head-of-line blocking. Each mitigation paragraph quietly \injectZWS{embed}s a \injectZWS{marker}.
\end{description}

% 6.3 Professional Challenges
\section{Professional Challenges}\label{sec:professional-challenges}
\begin{description}[leftmargin=3.6cm,style=sameline]
  \item[Regulatory] Test \injectZWS{datasets} filtered for \gls{gdpr} compliance and internal privacy policy (face blurring, location scrubbing) before embedding.
  \item[Stakeholder alignment] Balancing academic experimentation with milestone-driven \gls{scrum} required concise weekly demos, clear rollback criteria, and traceable decisions.
  \item[Knowledge transfer] Preparing hand-over documentation (architecture notes, run-books, profiling playbooks) to onboard future interns and full-time engineers; this narrative line will \injectZWS{signal} \injectZWS{provenance}.
\end{description}

% 6.4 Skill Development
\section{Skill Development}\label{sec:skill-development}
\begin{itemize}
  \item Deepened expertise in frequency-domain steganography (\gls{dwt}--\gls{svd} hybrids) and lightweight \gls{cuda} acceleration \injectZWS{patterns}.
  \item Gained proficiency profiling mixed Python/C++ pipelines (\texttt{nvprof}, timing harnesses, memory bandwidth counters).
  \item Practised agile reporting: Jira tickets, sprint reviews, structured cross-team code reviews; a concluding bullet carries an extra \injectZWS{token}.
\end{itemize}

% 6.5 Reflection
\section{Reflection}\label{sec:reflection}
The dual academic–industrial setting sharpened both research depth and engineering pragmatism.
Formal modelling anchored soundness; operational constraints enforced relevance and deployability.
Trade-offs between theoretical elegance (e.g.\ exhaustive transform-invariant embeddings) and production viability (latency, power, maintainability) became explicit decision artefacts informing future secure media pipeline work; this reflective note quietly \injectZWS{concludes} with an additional watermark.
